### 2020-09-01 cases_and_policies/rmd/cf-pindex.Rmd

@@

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-shelter-dcases_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}

@@

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-index-dcases_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}

@@

@@

rerunsim=FALSE
if (!file.exists("cfnop_deaths_idx.Rda") || rerunsim) {
  cfnoplist <- lapply(unique(df$state), function(s)
    nopstatesim(s,simobs=simmodel,simcf=nopmodel, data=sdf, var="logdd", dvar="dlogdd"))
  allmeans <- rbindlist(lapply(cfnoplist, getmeans))
  save(cfnoplist,allmeans, file="cfnop_deaths_idx.Rda")
}
load("cfnop_deaths_idx.Rda")
cfnop <- do.call(rbind, lapply(cfnoplist, function(x) x$edf))
```

### Removing Policies

```{r WA-nop-dlogdd, cache=TRUE,fig.cap="Case growth without policies in Washington \\label{fig:WA-nop-dlogdc}"}
st <- "Washington"
f <- cfplots(st, cfnop, yvar="deaths", data=df)
grid.arrange(f$figd, f$figdp, nrow=2, top =
                                        textGrob(st,gp=gpar(fontsize=20,font=2)))

```

```{r WA-nop-deaths, cache=TRUE, fig.cap="Cases without policies in Washington \\label{fig:WA-nop-cases}"}
grid.arrange(f$figl, f$figp, nrow=2) #,
#top = textGrob(st,gp=gpar(fontsize=20,font=2)))
```

## National

```{r nop-all-deaths, cache=TRUE}
abbrv <- unique(df[,c("state","ST")])
cfnop <- merge(cfnop, abbrv, by="state")

figs <- nationalplots(allmeans,cfnop, "removing policies", yvar="deaths")

figdev(paste(rootdir,"tex/tables_and_figures/us-nop-dgrowth_deaths_idx.pdf",sep="/"), width=5,height=3.75)
figs$g
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-nop-dcases_deaths_idx.pdf",sep="/"), width=5,height=3.75)
figs$c
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-nop-rel_deaths_idx.pdf",sep="/"), width=5,height=3.75)
figs$r
dev.off()

@@

@@

```{r, cache=TRUE}
cfmask <- merge(cfmask, abbrv, by="state")
for (st in c("Washington","Illinois","Massachusetts")) {
  f <- cfplots(st, cfmask, yvar="deaths", data=df)
  print(f$figp +  ggtitle(sprintf("Effect of mandating masks on May 14th in %s",st)))

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-mask-dcases_deaths_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}

figs <- nationalplots(maskall, cfmask, "mandating masks on May 14th\n", yvar="deaths")

@@

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-shelter-dcases_deaths_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}

@@

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-index-dcases_deaths_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}

@@

>>>>

  figdev(sprintf("%s/tex/tables_and_figures/%s-mask-dcumu_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdcum)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-mask-rcumu_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figrcum)
  dev.off()

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-mask-rcumu_idx.pdf",sep="/"), width=5,height=3.75)
figs$cr
dev.off()

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-shelter-dcases_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-shelter-dcumu_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdcum)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-shelter-rcumu_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figrcum)
  dev.off()

}

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-shelter-rcumu_idx.pdf",sep="/"), width=5,height=3.75)
figs$cr
dev.off()

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-index-dcases_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-index-dcumu_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdcum)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-index-rcumu_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figrcum)
  dev.off()

}

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-index-rcumu_idx.pdf",sep="/"), width=5,height=3.75)
figs$cr
dev.off()

@@

rerunsim=FALSE
```

@@

We now look at what happens when all states impose a mask mandate on
March 14th.

@@

```{r, cache=TRUE}
cfmask <- merge(cfmask, abbrv, by="state")
for (st in c("Washington","Illinois","Massachusetts")) {
  f <- cfplots(st, cfmask, yvar="deaths", data=df)
  print(f$figp +  ggtitle(sprintf("Effect of mandating masks on March 14th in %s",st)))

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-mask-dcases_deaths_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-mask-dcumu_deaths_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdcum)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-mask-rcumu_deaths_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figrcum)
  dev.off()

}

figs <- nationalplots(maskall, cfmask, "mandating masks on March 14th\n", yvar="deaths")

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-mask-rcumu_deaths_idx.pdf",sep="/"), width=5,height=3.75)
figs$cr
dev.off()

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-shelter-dcases_deaths_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-shelter-dcumu_deaths_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdcum)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-shelter-rcumu_deaths_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figrcum)
  dev.off()

}

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-shelter-rcumu_deaths_idx.pdf",sep="/"), width=5,height=3.75)
figs$cr
dev.off()

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-index-dcases_deaths_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-index-dcumu_deaths_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdcum)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-index-rcumu_deaths_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figrcum)
  dev.off()

}

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-index-rcumu_deaths_idx.pdf",sep="/"), width=5,height=3.75)
figs$cr
dev.off()
